Sustainable Indicators

### 2021-01-19 01-Sustainable-indicators.Rmd
adding the minmapping for all

# Intial Thougths
Quels indicateurs pour évaluer la soutenabilité: pertinence, disponibilité, facilité de mise en œuvre; s’accorcher au territoire: analyse des enjeux du territoire (périmètre thèse pavlo) =>

@@

<!-- Conceptual Framework -->
Nevertheless, there remain a gap in the scientific literature to define in what sense DRAM could be considered as sustainable transition in the global aspect of the term. 
The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
enhancing human well-being to more equitably meet the needs of both current and future generations.
@Clark2020 developed an integrative framework for sustainability considering five major pilards: 
(1) environment and development, 
(2) governance, 
(3) complexity, and 
(4) context dependence.

At the core of research on sustainability are the intertwined nature–society interactions.
Sustainability science research has focused on the four key elements involved in those interactions:

>>>>

# Initial Thougths
Quels indicateurs pour évaluer la soutenabilité: pertinence, disponibilité, facilité de mise en œuvre; s’accorcher au territoire: analyse des enjeux du territoire (périmètre thèse pavlo) =>

@@

<!-- Conceptual Framework -->
Nevertheless, there remain a gap in the scientific literature to define in what sense DRAM could be considered as sustainable transition in the global aspect of the term. 
The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
enhancing human well-being to more equitably meet the needs of both current and future generations.
@Clark2020 developed an integrative framework for sustainability considering five major pilards: 
(1) environment and development, 
(2) governance, 
(3) complexity, and 
(4) context dependence.
At the core of research on sustainability are the intertwined nature–society interactions.
Sustainability science research has focused on the four key elements involved in those interactions:
